\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
20210126-evaluations

Finally, we compute the approximation ratio of our greedy failure recovery algorithm, 
which is defined as dividing the optimal profit by the profit achieved. 
Figure \ref{approximation} shows that, 
our 2-approximation algorithm achieves a ratio between 1 and 1.25 in real scenarios, 
and the average profit loss is around 10\%.
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

@@

\begin{appendices}
     \section{Greedy algorithm for failure recovery} \label{B}
     \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}, a failure scenario $\bm{z}$} 
\KwOut{ $\{f^t_{d}\},F$}
Sort $d\in \hat{D}$ in non-decreasing order with $\frac{g_d}{\sum_{k\in K}\mathbf{b}^k_d}$;\\
$h_d=0, \forall d \in \hat{D}$; \\
$F=\{\}$;\\
\For{$d \in \hat{D}$}{
%$\{f'_{ikt}\},h_i,\{D_e\}\leftarrow$Allocation($F,i,B$);\\
%$h_d \leftarrow$ ;\\
\If { $\bm{z}$' s remaining capacity can support $d$}{
$h_d=1$;\\
    $F=F\cup {d}$;\\
    Update $\{f^t_{d}\}$;\\
   Update $\bm{z}$' s remaining network capacity;\\
}
\Else{
\If{$\sum_{d'\in F}g_{d'} <g_d$}{
\If {network resource allocated to demands in $F$ is able to support $d$}{
	release network resource allocated to demands in $F$;\\
     $F= \{d\}$;\\
    Update $\{f^t_{d}\},\forall d \in \hat{D}$;\\
    Update z’ s remaining network capacity;\\
$\bm{break}$; \\
}
}
\Else{
$\bm{break}$;
}

@@

Data loss due to failures is measured according to statistics reported by \textit{iperf} and switches.
As shown in Figure \ref{e2}(d), there is almost no loss in FFC, since it keeps a low network utilization. 
$\mathsf{BATE}$ has a slight loss caused by , while TEAVAR has the highest loss. 
\end{appendices}

>>>>

Finally, we compute the approximation ratio of our greedy failure recovery algorithm, 
which is defined as dividing the optimal profit by the profit achieved. 
Figure \ref{approximation} shows that, 
our 2-approximation algorithm achieves a ratio between 1 and 1.25 in real scenarios, 
and the average profit loss is around 10\% and it can save at least 90\% time (more details can be seen in Appendix \ref{testbed-appendix}).
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

@@

\begin{appendices}
     \section{Greedy algorithm for failure recovery} \label{B}
     \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}, a failure scenario $\bm{z}$} 
\KwOut{ $\{f^t_{d}\},F$}
Sort $d\in \hat{D}$ in non-decreasing order with $\frac{g_d}{\sum_{k\in K}\mathbf{b}^k_d}$;\\
$h_d=0, \forall d \in \hat{D}$; \\
$F=\{\}$;\\
\For{$d \in \hat{D}$}{
%$\{f'_{ikt}\},h_i,\{D_e\}\leftarrow$Allocation($F,i,B$);\\
%$h_d \leftarrow$ ;\\
\If { $\bm{z}$' s remaining capacity can support $d$}{
$h_d=1$;\\
    $F=F\cup {d}$;\\
    Update $\{f^t_{d}\}$;\\
   Update $\bm{z}$' s remaining network capacity;\\
}
\Else{
\If{$\sum_{d'\in F}g_{d'} <g_d$}{
\If {network resource allocated to demands in $F$ is able to support $d$}{
	release network resource allocated to demands in $F$;\\
     $F= \{d\}$;\\
    Update $\{f^t_{d}\},\forall d \in \hat{D}$;\\
    Update z's remaining network capacity;\\
$\bm{break}$; \\
}
}
\Else{
$\bm{break}$;
}

@@

Data loss due to failures is measured according to statistics reported by \textit{iperf} and switches.
As shown in Figure  \ref{appendix-e1}(b),
$\mathsf{BATE}$ and FFC have a slight loss caused by scheduling when failure occurs.
 while TEAVAR has the highest loss, because it might have congestion when rescaling.

\begin{figure}[t]
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/evaluation/time-consuming.pdf}
\caption{Time ratio}
\label{sim-time}
\end{center}
\end{figure}

We compute the time ratio of the optimal solution and our greedy failure recovery algorithm for each scenario.
Figure \ref{sim-time}  shows that the optimal solution which is derived by bruce force algorithm is at least 9 $\times$ larger than our greedy failure recovery algorithm.
\end{appendices}
